\plaintitle

### 2016-09-21 drafts/labor/piecework_lit.tex

@@

\subsection{Piecework and crowd work}

\msb{I assume this is forthcoming?}
Using the definition of piecework that we came up with earlier, we argue that
crowd work is fundamentally an instantiation of piecework, and
that we can more precisely anticipate the answers to the open research questions we discussed earlier.
We'll show that the dimensions of crowd work that the broader HCI community has been studying
align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
\subsection{From piecework to on--demand work}
Crowd work and gig work are fundamentally an instantion of piecework.
First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Third, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.

>>>>

Viewing crowd work as a modern instantiation of piecework is relatively straightforward by this definition. 
Platforms such as Mechanical Turk, Uber and TaskRabbit pay by the task, though some such as Upwork do offer hourly rates as well. 
% Second, workers on these platforms have significant freedom in choosing which tasks to work on, and when to log on and perform work~\cite{martin2014being,whyWouldAnyoneBrewer}. 
% Finally, computational workflows have successfully scaffolded many complex tasks into a series of small microtasks that can be performed without expertise.
%  \subsection{Piecework and crowd work}
% \msb{I assume this is forthcoming?}
% Using the definition of piecework that we came up with earlier, we argue that
% crowd work is fundamentally an instantiation of piecework, and
% that we can more precisely anticipate the answers to the open research questions we discussed earlier.
% We'll show that the dimensions of crowd work that the broader HCI community has been studying
% align with the history of piecework, and that this can greatly inform predictions about the future of crowd work.
% \subsection{From piecework to on--demand work}
% Crowd work and gig work are fundamentally an instantion of piecework.
% First, workers on platforms such as Mechanical Turk and Uber are generally incentivized by unit of work, even if some may be offered an hourly base salary as well.
Second, workers are attracted to these platforms by the freedom they offer to pick the time and place of work~\cite{martin2014being,whyWouldAnyoneBrewer}.
Finally, system developers as on Mechanical Turk typically assume no professional skills in transcription or other areas, and attempt to build that expertise into the workflow~\cite{noronha2011platemate,bernsteinSoylent}.

@@
